---
title: "Verification Analyses"
author: "Yuriy Sverchkov"
date: "3/30/2017"
output: html_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
resp.fgnem = readRDS("../results/respiration-fgnem.rds")
```

In this document we take the FGNEM learned from the respiration data and verify it against findings from the Nature Biotechnology paper.

## Identification of gene-specific phenotypes

The Y3K data set was systematically surveyed for effects that are specific to just one or two strains in the study.
These should correspond to effects that are attached to top 2 layers of the FGNEM

```{r gene-specific phenotypes}
#TODO. Look at Sup. Note 2, Sup. Tab. 4, Sup. Fig.s 5,6)
```

## Cliques in the FGNEM

Cliques in the FGNEM can be seen as clusters of knockouts, and we compare them to the clustering of profiles in the paper.

```{r respiration deficient strains}
# (Fig. 3c–f, Supplementary Fig. 8, Supplementary Note 4, and Supplementary Table 5).
# Supplementary Fig 9, Note 5, Supplementary table 6

# Y3K Identified a CoQ biosynthesis genes cluster that incuded uncharacterized yjr120w
# Also something about Atp2p


# Find cliques
findCliques = function ( acc ){
  
  nodes = rownames( acc )
  n = length( nodes )
  duplicates = rep( 0, n )
  names( duplicates ) = nodes
  
  for ( i in 1:(n-1) ) if ( duplicates[i] == 0 ) {
    candidate = acc[,i]
    for ( j in (i+1):n ){
      alternate = acc[,j]
      if ( all( alternate == candidate ) | all( alternate == -candidate ) )
        duplicates[i] = duplicates[j] = i
    }
  }
  
  clique_inds = unique( duplicates[ duplicates != 0 ] )
  
  Map( function ( i ){ names( which( duplicates == i ) ) }, clique_inds )
}

cliques = findCliques( resp.fgnem$acc )

"Cliques in the FGNEM:"
cliques
```

## Effect groups in the FGNEM

Effect groups in the FGNEM can be seen as clusters of molecules, and we compare them to the clustering of molecules by covariance

```{r effect groups}
# Look at Coq4p, PPHB
# Proteins in complexes (Cct2p, Cct7p)
# (Fig. 4b, Supplementary Fig. 11a, and Supplementary Table 8).
# These RDR-adjusted networks associated the MXP Yor020w-a with the mitochondrial ribosome (Supplementary Fig. 11g).
# To test this association, we examined the proteome of 􀀤yor020w-a yeast, which showed a significant (P < 0.05) decrease in the mitochondrial ribosome protein Rsm19p (Supplementary Fig. 11i), suggesting that Yor020w-a is linked to mitochondrial translation.
# (Fig. 4b, Supplementary Figs. 12 and 13). For example, the MXP Aim18p was linked to a network of CoQ biosynthesis proteins, and Aro9p and Aro10p were linked to numerous mitochondrial proteins that support oxidative phosphorylation (Fig. 4c–e).
# Also see last paragraph on page 5 of main text
```
